---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.height=6,
  fig.width=9, 
  dpi = 600, 
  out.width = "100%"
)
```

# Euro2020PassNetworks

<!-- badges: start -->
<!-- badges: end -->

This package provides UEFA Euro 2020 data, primarily focused on passing data.

## Installation

You can install the development version of Euro2020PassNetworks

``` r
require(remotes)
remotes::install_github("SinanPolatoglu/Euro2020PassNetworks")
```

## Data

There are two datasets included:

1. `MatchSummaries`: data frame overview stats for each match
2. `PassNetwork`: data frame containing `igraph` directed passing networks


```{r example}
library(Euro2020PassNetworks)
MatchSummaries
```
```{r}
PassNetworks
```

## Usage

Two helper functions are included to obtain lists of `igraph` objects: 

- `passes_by_match`
- `passes_by_team`

```{r}
bel_ita = passes_by_match('Belgium', 'Italy')
str(bel_ita, max.level = 1)
```

```{r}
ita = passes_by_team('Italy')
str(ita, max.level = 1)
```
Each `igraph` object is a directed graph of completed passes 
during a match with several node attributes on passing statistics. 
See `help("PassNetworks")` for details.

```{r}
bel_ita$Belgium
```

In combination with R's network analysis libraries, these passing 
networks can be interesting to get acquainted with network analysis.

```{r graph-bel, warning=FALSE, message=FALSE}
require(ggraph)
require(igraph)

G1 = bel_ita$Belgium
G2 = bel_ita$Italy

G1 = igraph::delete.vertices(G1, V(G1)$mins_played <= 70)
G2 = igraph::delete.vertices(G2, V(G2)$mins_played <= 70)

visualise_passes = function(G){
  set.seed(2020)
  ggraph(G, layout = 'fr')+
  geom_edge_fan(
    aes(width=completed_passes), arrow = arrow(length = unit(2, 'mm')),
    end_cap = circle(3, 'mm'), alpha = .5
  )+
  scale_edge_width(range = c(.1, 3))+
  geom_node_point()+
  geom_node_label(aes(label=gsub('^[[:alpha:]]+ ', '', name)), size=3, repel = TRUE) +
  theme_graph()
}

visualise_passes(G1)
```

```{r graph-ita, warning=FALSE}
visualise_passes(G2)
```


